---
output:
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: default
always_allow_html: yes
author: "Stephen Shiring"
title: "Variable Pagination Example"
date: "June 8, 2022"
---

## Fixed Slide #1

* This slide is fixed, it is specified in the RMarkdown document
* Content here may be dynamic; doesn't have to be.

* The outline of this example is: 3 fixed slides, 3 variable slides, 1 fixed slide, and 2 variable slides

\pagebreak

## Fixed Slide #2

* Another fixed slide

\pagebreak

## Fixed Slide #3 (Final)

* Final fixed slide
* Next three slides are programmatically-generated

\pagebreak

```{r, echo=FALSE, results='asis'}

library(ggplot2)
x = seq(0,10,0.1)

for (i in 1:3) {
  cat(paste0('\n## Variable Slide #',i,'\n'))
  
  # Some cheap logic to produce dynamic content  
  if (i == 1) {
    cat('* Content may be fixed or dynamic\n')
  } else if (i ==2) {
    cat('* Plot a sin(x)\n')
    cat('* We are getting a little bit ahead of ourselves with this example, but you must explicitly wrap the plot statement with /print() when making figures within a loop in order for them to be written\n')
    cat('* And don\'t forget to include a new line character at the end of each cat() statement!\n')
    print(qplot(x,sin(x),geom="path", xlab="time", ylab="Sine wave"))
  } else {
    cat('* Last variable page...\n')
    cat('* Plot sin(pi*x)\n')
    print(qplot(x,sin(pi*x),geom="path", xlab="time", ylab="Sine wave"))
  }
  
  cat('\n---\n')
}
```

## Fixed Slide #4

* Another fixed slide
* First after the previous variable slides section
* Next two slides are programmatically-generated

\pagebreak

```{r, echo=FALSE, results='asis'}
for (i in 4:5) {
  cat(paste0('\n## Variable Slide #',i,'\n'))
  cat('* Can also just have fixed content (not sure why this would be useful)\n')
  cat('\n---\n')
}
```
